Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-11-13 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Include captions, start to revise results, modify makefile
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2868 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 72fe968c18f11973e700543ec34dcf6356a417bf

\subsection{Results}
\fixme{update results section}
In order to test and compare the models over varying settings not only 1-hour but also 3-hour
forecasts are considered at both airports yielding four different scenarios of which the results
are discussed in this section.

@@

\begin{figure}[t]
\centering
\setkeys{Gin}{width=1.0\textwidth}
%\hspace{-2cm}
%\includegraphics{boxplot_crpsraw.pdf}
\includegraphics{_plot_circforest_validation_crpsraw_agg_comparison_with_lowff_v14b.pdf}
\caption{}
\label{fig:boxplot_crpsraw} 
\end{figure}

@@

\begin{figure}[t]
\centering
\setkeys{Gin}{width=1.0\textwidth}
%\hspace{-2cm}
%\includegraphics{boxplot_crpsskill.pdf}
\includegraphics{_plot_circforest_validation_crpsskill_agg_comparison_with_lowff_v14b.pdf}
\caption{}
\label{fig:boxplot_crpsskill} 
\end{figure}

>>>>

\subsection{Results}
\fixme{update results section}
This section provides a detailed analysis of the different proposed statistal models with focus
on their predictive performance. For a comprehensive comparison of the models, $1$\,hour and 
$3$\,h wind direction forecasts are evaluated at two airports, namely Innsbruck and Vienna, with
different meteorological site characteristics.

@@

\begin{figure}[t]
  \centering
  \setkeys{Gin}{width=1.0\textwidth}
  %\hspace{-2cm}
  %\includegraphics{boxplot_crpsraw.pdf}
  \includegraphics{_plot_circforest_validation_crpsraw_agg_comparison_with_lowff_v14b.pdf}
  \caption{CRPS skill scores for wind direction forecasts based on the full
    predictive von~Mises distribution for $+1$ and $+3$\,h forecasts at the
    airports Innsbruck and Vienna. Each box-and-whisker contains $24$~hourly scores
    per $12$~months averaged over the $5$~validation years; this yields a total of
    $288$~yearly mean values. The scores are shown for the reference models climatology, 
    persistence and the linear model, as well as for the circular regression tree and
    forest.}
  \label{fig:boxplot_crpsraw} 
\end{figure}

@@

\begin{figure}[t]
  \centering
  \setkeys{Gin}{width=1.0\textwidth}
  %\hspace{-2cm}
  %\includegraphics{boxplot_crpsskill.pdf}
  \includegraphics{_plot_circforest_validation_crpsskill_agg_comparison_with_lowff_v14b.pdf}
  \caption{As Figure~\ref{fig:boxplot_crpsraw}, but showing CRPS skill scores
    with the climatology model as reference. Skill scores are in percent; positive
    values indicate improvements over the reference.} 
  \label{fig:boxplot_crpsskill} 
\end{figure}
